---
title: "Poor Data Visual"
author: "RQuesT"
date: "`r Sys.Date()`"
output: 
    html_document:
        keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,
                      warning = F,
                      message = F)
```

### Overview

To visually convey why this dashboard failed, we will build a composite chart simulating the cluttered, overwhelming dashboard described in your text:

1. **Mock Data Generation**: Create a synthetic dataset representing 200 clinic pins with overlapping coordinates, multiple subtle shades of blue and orange, stacked stock statuses, and mock filter UI elements.

2. **Dense Scatter "Map"**: Plot overlapping clinic points with low contrast, hard-to-distinguish color tiers, and distracting grid-lines.

3. **Four Cluttered Stacked Bar Charts**: Show the fragmented view across 4 regions with multiple stacked stock layers.

4. **Mock Filter Controls**: Draw rectangular UI boxes representing the 6 tedious drop-down filters.

5. **Layout Assembly**: Align the pieces using standard `ggplot2` (leveraging facet/panel layouts or grob composition via grid/ggplot2 native tools).

### Complete R codes

#### 1. Load Required Libraries  

```{r libraries, include=TRUE}
library(dplyr)
library(ggplot2)
library(grid) # Base R package for grid layout view-port arrangement
set.seed(42) #Set seed for reproducible synthetic data
```

#### 2. Simulate Synthetic Dataset (200 Clinic Pins & Multilayer Attributes)

```{r dataSim}
n_clinics <- 200
bad_data <- tibble(
  clinic_id       = 1:n_clinics,
  long            = runif(n_clinics, min = 94.0, max = 98.5),
  lat             = runif(n_clinics, min = 15.0, max = 22.0),
  region          = sample(paste("Region", LETTERS[1:4]), n_clinics, replace = TRUE),
  vaccine_type    = sample(c("HepB", "BCG", "OPV", "Measles"), n_clinics, replace = TRUE),
  cold_chain      = sample(c("Solar", "Electric", "Passive Box"), n_clinics, replace = TRUE),
  # 4 confusing shades of blue and orange representing stock tier
  stock_tier      = sample(
    c("Tier 1", "Tier 2", "Tier 3", "Tier 4"),
    n_clinics,
    replace = TRUE
  ),
  stock_count     = sample(5:120, n_clinics, replace = TRUE)
)

# Palette with 4 poorly-distinguishable blues and oranges
confusing_colors <- c(
  "Tier 1"   = "#4A90E2",
  "Tier 2"   = "#2A52BE",
  "Tier 3" = "#E67E22",
  "Tier 4" = "#D35400"
)
```

#### 3. Component 1: Mock UI Dropdowns (The 6 Tedious Filters)

```{r uiSim}
filter_labels <- tibble(
  x = rep(c(1.5, 3.5, 5.5), 2),
  y = c(rep(2, 3), rep(1, 3)),
  label = c(
    "Region [All v]",
    "Vaccine Type [HepB v]",
    "Cold-Chain [Solar v]",
    "Stock Tier [Tier 1 v]",
    "Facility Type [All v]",
    "Reporting Week [Wk 34 v]"
  )
)
p_filters <- ggplot(filter_labels, aes(x = x, y = y)) +
  geom_tile(width = 1.8, height = 0.65, fill = "#F0F3F4", color = "#BDC3C7", size = 0.8) +
  geom_text(aes(label = label), size = 3, fontface = "bold", color = "#2C3E50") +
  xlim(0.3, 6.7) +
  ylim(0.4, 2.6) +
  labs(title = "Dropdown Filter Hell (6 Required Selections Before Insight)") +
  theme_void() +
  theme(
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5, margin = margin(b = 4))
  )
print(p_filters)
```

#### 4. Component 2: The Sprawling, Over-Plotted Map (200 Clinic Pins)

```{r overplotMap}
p_map <- ggplot(bad_data, aes(x = long, y = lat, color = stock_tier, shape = cold_chain)) +
  geom_point(size = 3.5, alpha = 0.85) +
  scale_color_manual(values = confusing_colors) +
  labs(
    title = "Sprawling Map View (200 Clinics Over-plotted)",
    subtitle = "Field supervisors spent 15 mins clicking filters (Stockout stuck at 18%)",
    x = "Longitude Coordinate",
    y = "Latitude Coordinate",
    color = "Stock Tier",
    shape = "Cold-Chain Model"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    plot.subtitle = element_text(size = 9, color = "red4"),
    panel.grid.major = element_line(color = "grey80", linetype = "dashed"),
    legend.position = "right",
    legend.box = "vertical",
    legend.title = element_text(size = 8, face = "bold"),
    legend.text = element_text(size = 7)
  )
print(p_map)
```

#### 5. Component 3: Four Cluttered Stacked Bar Charts

```{r clutterBar}
p_bars <- bad_data %>%
  group_by(region, vaccine_type, stock_tier) %>%
  summarise(total_stock = sum(stock_count), .groups = "drop") %>%
  ggplot(aes(x = vaccine_type, y = total_stock, fill = stock_tier)) +
  geom_col(position = "stack", width = 0.6) +
  facet_wrap(~ region, nrow = 1) +
  scale_fill_manual(values = confusing_colors) +
  labs(
    title = "Regional Vaccine Breakdown (4 Stacked Bar Sub-panels)",
    x = "Vaccine Type",
    y = "Doses",
    fill = "Stock Tier"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 11, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
    strip.text = element_text(face = "bold", size = 8),
    legend.position = "none"
  )

print(p_bars)
```

#### 6. Render Composite Dashboard to Canvas
```{r dashboard, fig.width= 8, fig.height=7}
# Open a new plotting page
grid.newpage()
# Define grid viewport layout: Filters (Top), Map (Middle), Stacked Bars (Bottom)
pushViewport(viewport(layout = grid.layout(nrow = 3, ncol = 1, heights = unit(c(1.2, 4.5, 3.2), "null"))))
print(p_filters, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(p_map,     vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(p_bars,    vp = viewport(layout.pos.row = 3, layout.pos.col = 1))
```

